Domain-Driven Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
Added missing word
Added transaction introduction

@@

\subsubsection{Transaction Times} \label{sec:transaction-times}
Transaction records consist of a customer, a store, a date and time, and a list of items purchased and their prices.

A transaction model is created for each customer and integrated over the simulation's timeframe to generate transactions.  Transactions are triggered when a customer runs out of items such as dog food as well as a random process describing the frequency of ``impromptu'' shopping trips.

@@

where $a_i$ is the amount of item category $i$ ``stuff'' remaining at time $t$. The variable $u_i$ gives the average usage rate and $\sigma^2_i$ gives the variance of the usage rate for item category $i$. The SDE is integrated using the Euler-Maruyama method \textcolor{red}{reference} with timestep $\Delta t_n$ sampled from a Poisson process:

@@

\subsubsection{Shopping Cart Items}

@@

The HMM could be extended to consider additional factors such as the amount of money spent so far in the transaction and the customer's spending habits.

\subsubsection{Other Fields}

>>>>

\subsection{Transactions}
A transaction model is created for each customer and integrated over the simulation's timeframe to generate transactions. Transaction records consist of a customer, a store, a date and time, and a list of items purchased and their prices.  The store is set to the store located closest to the customer. The date and time is given as a floating-point number with units of days since the start of the simulation.  (Timezones are not taken into account.)  Transaction times are generated from a Monte Carlo process based on the customer will use up items such as dog food (Section~\ref{sec:transaction-times}).  The purchased items are generated by a Hidden Markov Model (HMM) parameterized by the transaction time and amount of time remaining for the items in the customer's inventory (Section~\ref{sec:transaction-purchases}).

@@

\subsubsection{Transaction Times} \label{sec:transaction-times}

@@

where $a_i$ is the amount of item category $i$ ``stuff'' remaining at time $t$. The variable $u_i$ gives the average usage rate and $\sigma^2_i$ gives the variance of the usage rate for item category $i$. The SDE is numerically integrated using the Euler-Maruyama method \textcolor{red}{reference} with timestep $\Delta t_n$ sampled from a Poisson process:

@@

\subsubsection{Shopping Cart Items} \label{sec:transaction-purchases}

@@

The HMM can be extended to consider additional factors such as the amount of money spent so far in the transaction and the customer's spending habits.
